---
title: "PA1_template.Rmd"
output: html_document
---
####Loading and preprocessing the data
```{r}
setwd("C:/Study/Data Science Specialization/Reproducible Search/repdata_data_activity")
input <- read.csv("activity.csv")
```



####What is mean total number of steps taken per day?
the mean total number of steps taken per day is 10766.19
 , the median total number of steps taken per day is 10765 


####What is the average daily activity pattern?
```{r}
timeseries <- tapply(input$steps, input$interval, mean , na.rm=TRUE)
plot(rownames(timeseries), timeseries, type= "l" , xlab = "5-minute interval"
     , ylab = "the average number of steps taken")
```


####Imputing missing values
the no. of missing values is 2304
```{r}
sum(is.na(input$steps))
for (i in which(sapply(input, is.numeric))) {
  input[is.na(input[, i]), i] <- mean(input[, i],  na.rm = TRUE)
}

```



####Are there differences in activity patterns between weekdays and weekends?
yes, activity patterns in weekdays are greater than those in weekends
```{r}
day <- weekdays(as.Date(input$date))
input$day <-day
daylevel <- vector()
for (i in 1:nrow(input)) {
  if (day[i] == "ÇáÓÈÊ") {
    daylevel[i] <- "Weekend"
  } else if (day[i] == "ÇáÃÍÏ") {
    daylevel[i] <- "Weekend"
  } else {
    daylevel[i] <- "Weekday"
  }
}
input$daylevel <- daylevel
input$daylevel <- factor(input$daylevel)

require(lattice)
average_steps <- aggregate(steps~interval+daylevel, data=input, sum, na.rm = TRUE)
xyplot(steps ~ interval | daylevel, average_steps, type = "l", layout = c(1, 2), 
       xlab = "Interval", ylab = "Number of steps")

```




